### 2019-03-07 Revision2/Paper/app.tex
..

>>>>

\rebut{As shown in the PDF plotted in Figure~\ref{fig:pdf_36D}, the ignition delay assumes a wide range of values, i.e.
from about 2~ms to 400~ms. However, for many practical applications, a much smaller ignition delay (0.1~ms--1~ms) might
be of interest. The authors would like to point out that the proposed framework was also implemented to such a regime
by using a nominal value of the initial temperature, $T_0$ = 1000~K, and the initial pressure, $P_0$ = 1.5~atm. 
Our analysis for this
regime once again revealed that a 1-dimensional active subspace was able to capture the variability in the ingition delay due to
the uncertainty in the rate-controlling parameters and the input conditions. The sensitivity trends were also found to
be qualitatively similar to those presented in Figure~\ref{fig:as_36D}. We have not included these results in the interest
of brevity. Therefore, the proposed methodology was tested
for is robustness and applicability for a wide range of conditions pertaining to the considered application.}
